\newcommand*\showempentry[2]{\cventry#1{}{}{\begin{compactitem}#2\end{compactitem}}}
\DefineCategorisedSection{employmenthist}{Employment History}{\showempentry}{\item}


\newemploymenthist{bae.graduate}{
    {2021 - present}
    {Graduate Software Engineer}
    {BAE~Systems~Australia}
}{%
    \employmenthistitem{controlsystems}{Systems modeling using MATLAB and Simulink}
    \employmenthistitem{syseng}{Authoring of requirements and interface specification changes}
    \employmenthistitem{linux,programming}{Supporting execution of verification procedures prior to software releases}
    \employmenthistitem{linux}{Setup of virtualised development environments}
    \employmenthistitem{embedded,rtos}{Development and debugging of software for RTOS platforms}
}

\newemploymenthist{bae.intern}{
    {2020}
    {Engineering Intern}
    {BAE~Systems~Australia}
}{%
    \employmenthistitem{linux,programming}{Ongoing testing and development of mature mission critical software systems}
    \employmenthistitem{linux,programming}{Contribution towards fortnightly customer meetings}
    \employmenthistitem{electronics}{Analysis of replacements for obsolete components}
}

\newemploymenthist{consultant}{
    {2018 - 2019}
    {Engineering and IT Consultant}
    {}
}{%
    \employmenthistitem{linux,programming,embedded}{%
    Ported and enhanced embedded applications for the NetComm Bovine Linux platform.}
    \employmenthistitem{linux,sysadmin}{Setup of FreeIPA authentication systems.}
}

\newemploymenthist{kti.sysadmin}{
    {2015 - 2019}
    {Systems Administrator}
    {KTI~Pty~Ltd}
}{%
    \employmenthistitem{programming,python}{%
    Developed an integrated laser engraving utility using python, PyQt5, PyTest and SQLAlchemy.}

    \employmenthistitem{sysadmin}{%
    Development of several in house software applications including internal intranet, ERP system, product QA testing systems.}

    \employmenthistitem{sysadmin}{%
    Setup and maintained internal services and infrastructure including BIND-DNS, multi-gateway internet failover device (OpenWRT), OpenProject management software, WebERP accounting package and FreeIPA centralised authentication server.}
    
    \employmenthistitem{sysadmin}{%
    Managed on site VM environments including XenServer, VirtualBox, VMWare and Docker.}
    
}

\newemploymenthist{kti.processworker}{{2011 - 2015}{Process Worker}{KTI~Pty~Ltd}}{
    \employmenthistitem{manufacturing}{%
    Product serial number assignment and laser engraving.}
    
    \employmenthistitem{manufacturing}{%
    Soldering through hole and surface mount components.}
    
    \employmenthistitem{manufacturing}{%
    Battery pack tab welding, bottle fly-cutting, waterproof testing.}
}
