\documentclass[
    backaddress=false,
    foldmarks=false,
    fromalign=right,
    fromrule,
    fromphone,
    fromemail,
    parskip=half,
    refline=nodate
]{scrlttr2}

\usepackage{xcolor}

\areaset{\dimexpr\textwidth+5em\relax}{\dimexpr\textheight+\baselineskip*2\relax}

% First paragraph:
%   Which job I'm applying for, the company name, and where I found the advert.
% Second paragraph:
%   Why I'm interested in the position, company, products, services. Stress what I can do for
%   the employer. Recent graduate, explain how academic background makes me a solid candidate
%   for the position. Practical work experience should also be emphasized, specific achievements
%   etc. Not just a repeat of the same information as what will be found in the resume. Purpose
%   is to strengthen the resume with extra examples.
% Last paragraph:
%   Request a personal interview and indicate flexibility, time, and place. Repeat phone number.
%   End with a thankyou for considering my credentials.

\begin{document}
    \input{tex/letter-head.tex}
    \setkomavar{location}{\raggedleft\today}

    \addtoplength{firstheadvpos}{1em}
    \addtoplength{firstheadwidth}{2em}
    \addtoplength{toaddrhpos}{-1em}
    \setplength{sigbeforevskip}{0pt}
    \setplength{locvpos}{\useplength{toaddrvpos}+3.2em}
    \addtoplength{refvpos}{-3em}

    \renewcommand*\raggedsignature{\raggedright}

    \begin{letter}{%
        Emesent            \\
        1 Technology Court \\
        Pullenvale, QLD 4069}
        \opening{To whom it may concern,}
        I am writing to apply for the position of Software~Engineering~Intern at Emesent, as advertised on LinkedIn. I am a final year student of an electronic engineering and computer science double bachelors degree at Swinburne University of Technology. I believe that the knowledge I have gained during my time at Swinburne, along with prior experience from a systems administration role, make me an ideal candidate for the opportunity.

        Through past employments and pursuit of my degree at Swinburne, I have acquired a number of relevant skills and experiences. I have developed for a number of embedded Linux platforms including Netcomm's Bovine, and Raspbian. As part of university projects, I have also had hands on experience with IMUs, GPS and live video streaming using GStreamer/RTSP, and have just completed a unit on classical control systems. In my previous position at KTI, I also had hands on experience with developing a PyQt based laser engraving utility for production purposes.

        Given the opportunity, I would be thrilled at prospect of contributing towards Emesent's technology whilst also expanding my mathematical and technical abilities into the realm of 3D and LiDAR mapping. As such, I would welcome the opportunity to learn more about Emesent and to provide further insight into my abilities.

        Thank you for having the time to consider my credentials for this position, I look forward to hearing from you in due course.

        \closing{Sincerely,}
    \end{letter}
\end{document}
